Quality Definitions of Qualities

### 2020-02-03 StateOfPractice/QDefOfQualities/QDefOfQualities.tex
updated definitions

\begin{defn}
	 Verification is the process of evaluating a system or component to determine whether the products
	 of a given development phase satisfy the conditions imposed at the start of that phase \citep{IEEEStdGlossarySET1990}.
\end{defn}
\noindent \textbf{Proposed Definition}

Definition~\ref{Defn_Verifiability1} rephrased:
Verifiability is the extent to which a set of tests can be written and executed, to demonstrate
that the delivered system meets the specification.

>>>>

\begin{defn}
	 Verification is the process of evaluating a system or component to determine whether the products
	 of a given development phase satisfy the conditions imposed at the start of that phase \citep{IEEEStdGlossarySET1990}.
\end{defn}

\begin{defn}
	Verifiability refers to how well software components or the integrated
	product can be evaluated to demonstrate whether the system functions as
	expected \citep{wiegers2003softreq}.
\end{defn}
\noindent \textbf{Proposed Definition}
Definition~\ref{Defn_Verifiability1} rephrased:
Verifiability is the extent to which a set of tests can be written and executed, to demonstrate
that the delivered system meets the specification.
